Visual proteomics using whole-lamella 2D template matching

### 2022-02-25 manuscript.tex
Remove tex file [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/c726b59baf4d652934928fac32dda6261f8cf435.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/c726b59baf4d652934928fac32dda6261f8cf435/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1899284881

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/1e239da5dfa82be752529df88887c5cf4896c57d/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/1e239da5dfa82be752529df88887c5cf4896c57d}{jojoelfe/deco\_lace\_template\_matching\_manuscript@1e239da}
on February 24, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/c726b59baf4d652934928fac32dda6261f8cf435/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/c726b59baf4d652934928fac32dda6261f8cf435}{jojoelfe/deco\_lace\_template\_matching\_manuscript@c726b59}
on February 25, 2022.
